Well-quasi-orderings on word languages

### 2024-08-19 src/infixes.tex
characterizing chains for the infix relation

>>>>

Let us conclude this section by fully characterizing what are
actually the chains for the \kl{infix} relation, without any 
regularity assumption.

\begin{lemma}
    \label{chains-infix:lem}
    Let $L$ be a \kl{chain} for the \kl{infix relation}. Then, there exists
    a \kl{chain} $P$ for the \kl{prefix relation} and a \kl{chain}
    $S$ for the \kl{suffix relation} such that $L \subseteq SP$.
\end{lemma}
\begin{proof}
    Because $L$ is a chain,
    we have an enumeration $L = \seqof{w_n}$,
    where $s_n \defined \card{w_n}$ is increasing, 
    and functions
    $f_{i,j} \colon \set{1, \dots, s_i} \to \set{1, \dots s_{j}}$
    satisfying
    that $f_{j,k} \circ f_{i, j} = f_{i, k}$,
    $f_{i,i} = \mathrm{id}$, and
    $w_i = w_j[f_{i,j}(1):f_{i,j}(s_i)]$ for all $i \leq j$.
    Now, we can build the infinite word $w_\infty$ indexed by $\Zel$, and
    embeddings $f_{i, \infty} \colon \set{1, \dots, s_i} \to \Rel$ such that
    $w_i = w_\infty[f_{i, \infty}(1):f_{i, \infty}(s_i)]$, and $f_{i, \infty}
    \circ f_{j, i} = f_{j, \infty}$ for all $i \leq j$.

    Let us define $w_l$ as the (infinite) word $w_\infty[-\infty: f_{0,
    \infty}(s_0)]$ and $w_r$ as the (infinite) word $w_\infty[f_{0,
    \infty}(s_0): +\infty]$. It is now clear that every word $w_i$ can be
    written as $w_i = w_{i,l} w_{i,r}$, where $w_{i,l}$ is a prefix of $w_r$
    and $w_{i,r}$ is a suffix of $w_l$. Furthermore, the functions $f_{i,
    \infty}$ can be used to notice that $\seqof{w_{i,r}}$ is a \kl{chain} for
    the \kl{prefix relation}, and $\seqof{w_{i,l}}$ is a \kl{chain} for the
    \kl{suffix relation}, which allows us to conclude.
\end{proof}
